Analysing Melbourne CBD pedestrian counts data with a focus on imputation methods

### 2017-10-22 thesis_draft/02-chap2.Rmd
acknowledgements

>>>>

Implementation of the imputation algorithm was made such that it is efficient, reproducible and general enough to allow for changes to model parameterisation and new data with from new sensor installations.

Using the imputed data, a predictive model to be used for point estimates for a given time was built and packaged in a function in R, `ped_predict()`, to facilitate predictions in an easy and tidy format. The model has been saved so that predictions can be made without the end user needing to estimate the model prior to prediction.
